% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
% Figures should be included in EPS format
\usepackage{float}

\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm} %bold italic maths with \bm
\usepackage{mleftright}

\newcommand{\equ}{\mathrel{\Leftrightarrow}}
\newcommand{\lnb}[1]{\ln\mleft( #1 \mright)}
\newcommand{\logb}[1]{\log\mleft( #1 \mright)}
\newcommand{\expb}[1]{\exp\mleft( #1 \mright)}
\newcommand{\fct}[1]{#1!\,}
\newcommand{\TP}{\mathit{TP}}
\newcommand{\FP}{\mathit{FP}}
\newcommand{\TN}{\mathit{TN}}
\newcommand{\FN}{\mathit{FN}}
\newcommand{\TPR}{\mathit{TPR}}
\newcommand{\TNR}{\mathit{TNR}}
\newcommand{\TTD}{\mathit{TTD}}
\newcommand{\Fitness}{\mathit{Fitness}}
\newcommand{\fmeasure}{f_{\mathit{measure}}}
\newcommand{\fdetect}{f_{\mathit{detect}}}

\newcommand{\R}[1]{\mathcal{#1}} % random variable
\newcommand{\M}[1]{\mathbf{#1}} % matrix
\newcommand{\V}[1]{\bm{#1}} % vector

%\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
%\DeclareMathOperator*{\diag}{diag}
\DeclareMathOperator*{\sign}{sign}
\DeclareMathOperator*{\clip}{clip}
\DeclareMathOperator{\lsp}{lsp}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}
\makeatletter
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
\makeatother

%\newtheorem{definition}{Definition}

\usepackage{hyperref}
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}

\title{Adversarial Attacks on Leakage Detectors in Water Distribution Networks}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Paul Stahlhofen \and
Andr\'e Artelt\orcidID{0000-0002-2426-3126} \and
Luca Hermes\orcidID{0000-0002-7568-7981} \and
Barbara Hammer\orcidID{0000-0002-0935-5591}}
%
\authorrunning{P. Stahlhofen, A. Artelt, L. Hermes, B. Hammer}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Bielefeld University, Inspiration 1, 33615 Bielefeld, Germany
\email{\{pstahlhofen,aartelt,lhermes,bhammer\}@techfak.uni-bielefeld.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Many Machine Learning models are vulnerable to adversarial attacks: There
exist methodologies that add a small (imperceptible) perturbation to an input such that the model comes up with a wrong prediction. Better understanding of such attacks is crucial in
particular for models used in security-critical domains, such as monitoring of water distribution networks, in order to devise
counter-measures enhancing model robustness and trustworthiness.

We propose a taxonomy for adversarial attacks against machine learning based leakage detectors in water distribution networks. Following up on this, we focus on a particular type of attack: an adversary searching the
\textit{least sensitive point}, that is, the location in the water network where the
largest possible undetected leak could occur. Based on a mathematical
formalization of the least sensitive point problem, we use three different
algorithmic approaches to find a solution. Results are evaluated on two
benchmark water distribution networks.
\keywords{Adversarial Attacks  \and Water Distribution Networks \and Leakage
Detectors.}
\end{abstract}
%
%
%
\section{Introduction} % including related work
\input{introduction.tex}
\section{Foundations}
\label{sec:foundations}
\subsection{Adversarial Attacks}
\input{basic_adversarials.tex}
\subsection{Leakage Detection in Water Distribution Networks}
\input{leakage_detection.tex}
\section{Adversarials in Water Distribution Networks}
\label{sec:adversarials_in_wdns}
\subsection{Taxonomy of Adversarials in WDNs}
\input{taxonomies.tex}
\subsection{The Least Sensitive Point Problem}
\input{problem_definition.tex}
\subsection{Algorithmic Approaches}
\input{algorithmic_approaches.tex}
\section{Case Study: LSP Search in Two Benchmark Networks}
\label{sec:case_study}
\subsection{Leakage Detector}
\input{between_sensor_interpolator.tex}
\subsection{Water Networks}
\input{networks_and_data.tex}
\section{Results and Discussion}
\label{sec:results}
\subsection{Hanoi Network}
\input{hanoi.tex}
\subsection{L-Town Network}
\input{ltown.tex}
\section{Conclusion}
\label{sec:conclusion}
\input{conclusion.tex}

\paragraph{Acknowledgements}
We gratefully acknowledge funding from the European Research Council (ERC)
under the ERC Synergy Grant Water-Futures (Grant agreement No. 951424).
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{adversarials_vs_detectors.bib}
%
\end{document}
